\subsection{FACTOR}
\subsubsection{Functionality}
\begin{itemize}
    \item Enable users to submit votes
    \item Administrative overriding of playlist ordering
    \item Limit the track space the users can search in, at any given time
    \item View history of played tracks
    \item Playback of tracks
\end{itemize}

\subsubsection{Application Domain}
\begin{itemize}
    \item Administration of tracks and request
    \item The order of the tracks on the playlist
    \item Playback of the playlist
\end{itemize}

\subsubsection{Conditions}
\begin{itemize}
    \item The client should be minimalistic, so as to improve understandability and learnability, even for intoxicated users.
    \item Limitation of what music is allowed at the venue
    \item Has to keep track of what users are on location
\end{itemize}

\subsubsection{Technology}
\begin{itemize}
    \item Smartphones
    \item Computer (local server)
    \item Internet
    \item Digital music library
\end{itemize}

\subsubsection{Objects}
\begin{itemize}
    \item Tracks
    \item Votes
    \item Users
    \item Playlist
    \item Filter
    \item Admin
\end{itemize}

\subsubsection{Responsibility}
\begin{itemize}
    \item User influence on music playback
    \item Administrative control for the venue
\end{itemize}

\subsection{System Definition}
An information system enabling venues to have guests vote for tracks to be played. The system should enable the administrators to override the specific tracks and limit the track space the users can vote for, at any given time. The client should be minimalistic, so as to improve understandability and learnability, even for intoxicated users. The system should display already requested tracks to all customers to improve discoverability. The system should be able to continuously play music, even with no user input, in order to increase continuity and autonomy.
The administrative server has to be able to run on an inexpensive computer with a varying stability of internet access and access to a music catalogue. The client application has to run on smartphones with varying internet access.
