Rockbot is a service where brands and enterprises can create venues at their locations. People who are at the location of these venues can vote on songs from a predetermined playlist and see what is playing and will be played. The system uses GPS data to find the users position and find out what venues the user are able to check in at \cite{rockbotFeatures}.

All users can add songs to the playlists from the approved library but when their song is played is affected by their DJ level. This level is decided from the users activity over a 120 day period. Their activity is decided from number of picks made, number of check-ins and number of likes \cite{rockbotBlog}.

The concept behind this is that users add songs to a playlist dynamically and rewarded by doing so, by introducing the concept of having a level system, to give a sense of progression to encourage the user to utilise the system. For the user to be able to affect the playlist, one must check in using a location service. The leveling system affect the position the individual users songs on playlist when added to playlist, by how much they use the system at the checked in location. The concept of having to check in ensures that users who are not on site can utilise the system.
As a requirement by the bars in the interviews being to control what themes or genres of music to played, the system has achieved this throught the strict concept of the libary being predetermined, which means the users cannot add songs to playlist which is not in the approved libary. 