SecretDJ~\cite{secretDJ} is a mobile app that enables you choose the tunes that play in bars and pubs. The app gives its users the ability to see which venues use the SecretDJ system, and which are nearest to the user. The users can add tracks to the venue's playlist and give likes, via Facebook, to the tracks, moving them up the playlist.

A new user can add four tracks to a venue's playlist each day. If a user gets a lot of likes for the tracks he has added to a venue's playlist, the user can rise in rank for that venue, which means the user can add more tracks to that venue's playlist and that his choices are moved further up the playlist by default.

If a user gets enough likes and is active enough, the user can rise to the rank of DJ for a venue, meaning that the user's choice of tracks will always be next in line, and there is no limit to the amount of tracks the DJ can add to the playlist.

A concept of having a master service to give the users an overview over what tracks are playing and will be played at multiple venues near the user, which is benificial for user if the user is scouting for a bar with his music preferences. The system intergrates a social media for voting on track, this concept could be discouraging to some users if the user didnt want to share ones music preferences. The user has the ablities to add and vote on tracks on the playlist, adding track to the playlist is limited by a daily number of entries, determined by a level system based on the number likes the tracks he added to playlist, got by other users of the system. A concept of one user becoming a dj, hence the name SecretDJ, is achievable by being the most active and liked user at the venue, which gives the power of unlimited adding to the playlist and all the DJ's track is next in queue, this could cause potential problem in that other users tracks are neglected until the DJ leaves the venue, making it hard anybody else to progress in their level.
