\chapter{Analysis}

This section analyses the initial problem described in the introduction. The analysis methods used originates from \cite{mathiassen2001objektorienteret}. 

\section{Problem Domain \& Application Domain}

\sinote{Dette afsnit er design orienteret. Er ikke færdigt}

\textbf{Problem domain}: \enquote{That part of a context that is administrated, monitored or controlled by a system.}

\begin{description}
  \item[Songs] The songs that are available for playing.
  % \item[Playlists] Collections of songs centered around a specific theme.
  \item[Votes] Some mechanism for choosing which songs to play next.
  \item[Users] Data and statistics of the users of the system.
  \item[Places] What is playing at particular places?
  \item[Audio system] Plays the chosen song.
  \item[Display system] Displays queue, current song, etc. at the installation site.
\end{description}

\textbf{Application domain}: \enquote{The organization that administrates, monitors, or controls a problem domain.}

\begin{description}
  \item[Users] The users of the application chooses which songs to play next.
  \item[Frontend] Provides control of songs, playlists and users.
  \item[Backend] Administrates and monitors users of the application. Communicate with the audio- and display system.
\end{description}

\section{Architecture}
\label{sec:architecture}

\sinote{Dette afsnit er design orienteret. Er ikke færdigt}

Model:

Songs:
\begin{itemize}
  \item Current song
  \item Queue
  \item Song repertoire
\end{itemize}

Votes:
\begin{itemize}
  \item Upvotes
  \item Downvotes
  \item Master override
\end{itemize}

Users:
\begin{itemize}
  \item Votes statistics. Affects user's influence
\end{itemize}

\input{Chapters/Analysis/StateOfTheArt/SecretDJ.tex}
