There are generally two ways to interact with a system. In this project, they are defined as centralised or decentralised interaction.

Centralised interaction means that communication has to flow through a single point and is how most venues currently work.

Decentralised interaction means that communication is not dependent on a single point, but instead is possible from multiple points.

Most venues currently rely on a centralized interaction form. In most cases this is bartenders or waiters working at the venue. Venues require this form of centralized interaction because of the need to maintain control of the music being played. However by taking this centralized approach to interaction, the bartenders or waiters need to dismiss time from their primary tasks to interact with users.

When working with user interaction there are two main considerations; how the user receives data (input) and how the user influences the system (output).

% Currently the user can interact with the system via a centralized system where all users can interact at one or few interaction points. The alternative to this is a decentralized interaction point system where each user can interact with the system via individual interaction points.

The input for the user can either be centralised e.g. a monitor at a central location, or decentralized e.g. the user's smartphone showing the input.

The user can also influence the system either centralised, e.g. by communicating with venue workers, or decentralized, e.g. by interacting with the user's smartphone.

Systems can mix and match their interaction forms i.e. decentralised from the user to the system, but centralized from the system to the user.

% The same two possibilities goes for the input to the user. Meaning that the input, the user being able to see the result of his or her interaction, can either be centralized combining the interaction from all the users in one place and displaying it there or decentralized, showing the result for his or her interaction and possibly the combined interaction from all too.

% Furthermore both the input and output interaction points can be combined meaning that the system could either have a completely centralized interaction point or completely decentralized interaction points enabling the users to both interact with the system and recieve conformation at the same point.