%intro til System Description
To concretise the system which is described in this report, this section will present a detailed description of the specification of the system. This section will include a FACTOR analysis, a hallmark of object oriented analysis and design, and a system definition, which will pave the way for the remainder of the report.

\subsection{FACTOR}
\label{FACTOR}
FACTOR is a list of criteria that can be used in the process of creating a system definition. A FACTOR was created through the current knowledge of the system. This was done to list and organise the system and domain of where the system should be implemented.

This was created on the basis of \citetitle{sorensen2012}~\cite{sorensen2012}, adding additional concepts from the rest of the state of the art confirmed by requirements from both the guests and administrators, found in \cref{sub:administersinterviews} and \cref{userInterviews}, or otherwise argued for.
\subsubsection{Functionality}
\label{subsub:functionality}
The functionality is what the system should be able to do. These are mainly formed from the requirements, given by both the administrators and guests.
\begin{itemize}
    \item Enable users to submit votes. Building on the base principle of \citetitle{sorensen2012}~\cite{sorensen2012}, described in \cref{MDCI}, users should be able to interact with the system, in order to cater to their music preferences. This was also confirmed by guests of a venue, as a good idea in \cref{ProposalsForGuestControlledMusic}. From the principle of voting in \cref{Voting}, it was chosen that the best way to do this fairly and dynamically (see \cref{sub:problemStatement}) was through votes. This was done, since votes enable every user to have the possibility to have equal say in what is to be played, while still rewarding more active users, hence fair and equal possibilities for all guests. This also makes it possible to implement dynamic voting since votes can be changed or reset as desired.
    \item Administrative overriding of playlist ordering. This concept was described in \cref{AdministrativeEditingofPlaylist} and was decided to be used from the requirements, found in the interviews with administrators, described in \cref{sub:administersinterviews}.
    \item Limit the track space which the users can search in, at any given time. This principle was described in \cref{sub:auto_rearrange_playlist}. This concept is included, due to the requirements in \cref{sub:administersinterviews}.
		\item Ensure continuous playback of music. One criteria for the system in \citetitle{sorensen2012}~\cite{sorensen2012} was that the music should never stop playing. This was also confirmed in the interviews, expressed in \cref{sub:specific_remarks}, where all bars expressed that the music should not stop playing, unless it was intentional from the administrators, even if the playlist was empty and/or no one had voted for anything. An extension of this concept was found in \cref{sub:auto_rearrange_playlist}, where the application Mixgar automatically adds tracks to the playlist from analysing the party’s mood curve from the users votes, social media accounts and the previously played tracks. This will be looked further into in \cref{sec:algorithm}.
    \item View history of played tracks. A history is modelled in the system to keep track of what has been played. This could be used to keep track of the flow of the music, to ensure music continuity or as an extended service for the users and administrators, so they can see what has been played.
		\item View the current playlist. The playlist is central for the system; it is what the guests can affect though votes and, since it is the order of the tracks, what the administrators want to control and make sure follows the venues interests. It is therefore very important to keep track of this and be able to view it.
    \item Playback of tracks.
\end{itemize}

\subsubsection{Application Domain}
The application domain describes work flows of the administrators. These were determined from the concepts, described in \cref{StateOfTheArt} and confirmed in interviews made with administrators in \cref{sub:administersinterviews}.
\begin{itemize}
    \item Restrict tracks
		\item Reorder and edit the playlist
    \item Play, pause and stop music
\end{itemize}

\subsubsection{Conditions}
These are the conditions for, either the development or usage of, the system. These were either found, in the interviews in \cref{sub:administersinterviews,userInterviews}, or dictated, by the environment, dictated by the concepts in \cref{StateOfTheArt}.
\begin{itemize}
  \item The client should be minimalistic, so as to improve understandability and learnability, even for intoxicated users
	\item The client should be accessible for a wide target group
	\item The system should support multiple users concurrently
	\item The system should be developed in collaboration with administrators of a venue
\end{itemize}

\subsubsection{Technology}
The technology needed for the system to be fully functional.
\begin{itemize}
    \item Smartphone, used to interact with the system
    \item Computer, used for playing music and storing the playlist, history and votes
		\item Situated display, used for the presentation interface
    \item Internet
    \item Digital music catalogue
\end{itemize}

\subsubsection{Objects}
\label{FACTORObjects}
The objects modelled in the problem domain.
\begin{itemize}
  \item Track
  \item Vote
  \item Guest
  \item Playlist
  \item History
  \item Restriction
  \item Administrator
\end{itemize}
Requests are not modelled as a object for itself. A unifying concept of vote and request was derived from the ideas of voting and requesting from \cref{StateOfTheArt}. In this concept, votes and request are the same thing. This is done by perceiving all tracks in the music catalogue of the venue, as being eligible for votes, but only tracks with at least one vote will be put on the playlist. This voids the need for requests, while still keeping the functionality, and simplifying the whole system. For these reasons, the rest of the project will work under this unified concept, and will refer to user requests as votes.

\subsubsection{Responsibility}
The responsibility the system will have in the context of a venue.
\begin{itemize}
  \item User influence on music playback
  \item Administrative control and restriction, for the venue
\end{itemize}

\newpage
\subsection{System Definition}\label{sub:systemDefinition}
From the FACTOR analysis, a formal system definition was created,
clearly defining the system. This definition is used as the basis for
the rest of the project.

\begin{center}
\textit{An information system, enabling venues to have guests vote for tracks to be played. The system should enable the administrators to override the specific tracks and limit the track space the users can vote for, at any given time. The system should support multiple users concurrently and be able to display already requested tracks to all customers, so as to improve discoverability. The server should be able to continuously play music. The server has to be able to run on an inexpensive computer, with access to a music catalogue and an internet connection of varying stability. The client application has to be able to run on smartphones with unstable internet access, limited data traffic and limited battery capacity, while being accessible for a wide target group. The client should be minimalistic, so as to improve understandability and learnability, even for intoxicated users.}
\end{center}
